---
title: "Lab 5"
author: "Ridhima chaudhuri"
date: "10/25/2021"
output: 
  html_document: 
    theme: cerulean
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence interval

In this section, we will use the 't.test()' function to calculate the confidence interval

### Example 1

Create a single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too


```{r}

# create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval:

otter_ci <- t.test(otter_lengths)


# Find the standard deviation

otter_sd <- sd(otter_lengths)
```

the mean otter length is 36.9 inches  $\pm$ 9.3 (mean $\pm$ sd, n=8) with a 95% confidence interval of [29.1, 44.7] inches. 


#### now, using inline referencing

Mean otter length is `r otter_ci$estimate `


Mean otter length is `r round(otter_ci$estimate,1) ` inches




